Inferring disease architecture and predictive ability\\with LDpred2-auto

### 2023-06-08 paper/paper-infer-supp.tex
small modifs

\begin{figure}[p]
	\centerline{\includegraphics[width=0.85\textwidth]{est_h2_one_200K}}
	\caption{Inferred SNP heritability $h^2$ in simulations with continuous outcomes and N=200K. Horizontal dashed lines represent the true simulated values. 
		For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
		``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}.
		The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $h^2$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS). The 95\% confidence interval for the LD Score (LDSc) regression estimate is obtained as $\pm$1.96 of its standard error.  \label{fig:simu_h2_large}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=0.9\textwidth]{est_p_one_20K}}
\caption{Inferred polygenicity $p$ in simulations with continuous outcomes and N=20K. Horizontal dashed lines represent the true simulated values. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $p$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS).\label{fig:simu_p}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.9\textwidth]{est_p_one_200K}}
	\caption{Inferred polygenicity $p$ in simulations with continuous outcomes and N=200K. Horizontal dashed lines represent the true simulated values. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
		``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
		The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $p$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS).\label{fig:simu_p_large}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=0.8\textwidth]{est_alpha_one_20K}}
\caption{Inferred $\alpha$ in simulations with continuous outcomes and N=20K. Horizontal dashed lines represent the true simulated values. Horizontal dotted lines represent boundaries imposed on the LDpred2-auto estimates. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that ``LDpred2\_noMLE'' (\texttt{use\_MLE = FALSE}) does not infer $\alpha$. Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $\alpha$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS).\label{fig:simu_alpha}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.8\textwidth]{est_alpha_one_200K}}
	\caption{Inferred $\alpha$ in simulations with continuous outcomes and N=200K. Horizontal dashed lines represent the true simulated values. Horizontal dotted lines represent boundaries imposed on the LDpred2-auto estimates. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that ``LDpred2\_noMLE'' (\texttt{use\_MLE = FALSE}) does not infer $\alpha$. Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
		The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $\alpha$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS).\label{fig:simu_alpha_large}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{postp_calib}}
\caption{Calibration of per-variant posterior probabilities of being causal (also known as posterior inclusion probabilities) in simulations with continuous outcomes. These probabilities are binned on a log-scale, and mean in each bin is compared to the proportion of simulated causal variants in the bin (with 95\% CI). Green dashed lines represent the 1:1 line. Only results for $\alpha = -0.5$ and \texttt{allow\_jump\_sign = FALSE} are represented. \label{fig:simu_postp_calib}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{local_h2_calib}}
\caption{Calibration of per-block heritability estimates in simulations with continuous outcomes. 
Local $h^2$ estimate for each block is compared to the true simulated local heritability in the block.
Green dashed lines represent the 1:1 line. Only results for $\alpha = -0.5$ and \texttt{allow\_jump\_sign = FALSE} are represented. \label{fig:simu_h2_calib}}
\end{figure}

@@

\begin{figure}[p]
\centerline{\includegraphics[width=0.9\textwidth]{est_r2_one_20K}}
\caption{Inferred predictive performance $r^2$ in simulations with continuous outcomes and N=20K. Green segments represent $r^2$ in the test set. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. \label{fig:simu_r2}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.9\textwidth]{est_r2_one_200K}}
	\caption{Inferred predictive performance $r^2$ in simulations with continuous outcomes and N=200K. Green segments represent $r^2$ in the test set. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
	``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. \label{fig:simu_r2_large}}
\end{figure}

@@

\begin{figure}[p]
	\centerline{\includegraphics[width=0.83\textwidth]{est_binary_h2_one}}
	\caption{Inferred SNP heritability $h^2$ in simulations with binary outcomes. Horizontal dashed lines represent the true simulated values. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the $h^2$ estimates from the iterations (after burn-in) of the chains kept. The 95\% confidence interval for the LD Score regression estimate is obtained from $\pm$1.96 times its standard error. {\NEFF} All $h^2$ estimates are transformed to the liability scale with K\_pop=K and K\_GWAS either K (the simulated prevalence) or 0.5 (when using Neff) using function \texttt{coef\_to\_liab} from R package bigsnpr \cite{lee2012better,prive2017efficient}. \label{fig:simu_h2_bin}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.9\textwidth]{est_binary_p_one}}
	\caption{Inferred polygenicity $p$ in simulations with binary outcomes. Horizontal dashed lines represent the true simulated values. {\NEFF} \label{fig:simu_p_bin}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.83\textwidth]{est_binary_alpha_one}}
	\caption{Inferred $\alpha$ in simulations with binary outcomes. Horizontal dashed lines represent the true simulated values. Horizontal dotted lines represent boundaries imposed on the estimates. {\NEFF} \label{fig:simu_alpha_bin}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.88\textwidth]{est_binary_r2_one}}
	\caption{Inferred predictive performance $r^2$ in simulations with binary outcomes. Green segments represent $r^2$ in the test set. {\NEFF} All $r^2$ estimates are transformed to the liability scale with K\_pop=K and K\_GWAS either K (the simulated prevalence) or 0.5 (when using Neff) using function \texttt{coef\_to\_liab} from R package bigsnpr \cite{lee2012better,prive2017efficient}; the ones from the test set are transformed with K and K. \label{fig:simu_r2_bin}}
\end{figure}

@@

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2}}
	\caption{SNP heritability estimates from either LDpred2-auto or LD Score regression for all 248 phenotypes defined from the UK Biobank. These are stratified by the polygenicity estimated from LDpred2-auto. Green dashed lines represent the 1:1 line. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the $h^2$ estimates from the iterations (after burn-in) of the chains kept. The 95\% confidence interval for the LD Score regression estimate is obtained from $\pm$1.96 times its standard error.  ``use\_mle: TRUE'' corresponds to using the new 3-parameter model and sampling scheme (Methods). \label{fig:ukbb_h2}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2_p}}
	\caption{Estimates from LDpred2-auto for either the SNP heritability $h^2$ or the polygenicity $p$ for all 248 phenotypes defined from the UK Biobank. Estimates of $h^2$ are constrained to be at least 0.001, and at least $10^{-5}$ for $p$. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the estimates from the iterations (after burn-in) of the chains kept. \label{fig:ukbb_h2_p}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2_alpha}}
	\caption{Estimates from LDpred2-auto for either the SNP heritability $h^2$ or $\alpha$ for all 248 phenotypes defined from the UK Biobank. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the estimates from the iterations (after burn-in) of the chains kept. We only show phenotypes for which there are more than 25 chains kept, because simulations have shown that $\alpha$ estimates are unreliable when a small number of chains is kept (Figure \ref{fig:simu_alpha}). \label{fig:ukbb_h2_alpha}}
\end{figure}

>>>>

\begin{figure}[p]
	\centerline{\includegraphics[width=0.85\textwidth]{est_h2_one_200K}}
	\caption{Inferred SNP heritability $h^2$ in simulations with continuous outcomes and N=200K. Horizontal dashed lines represent the true simulated values. 
		For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
		``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}.
		The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $h^2$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS). The 95\% confidence interval for the LD Score (LDSc) regression estimate is obtained as $\pm$1.96 of its standard error. Colors for LDpred2 models represent the number of chains kept (out of 50).  \label{fig:simu_h2_large}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=0.9\textwidth]{est_p_one_20K}}
\caption{Inferred polygenicity $p$ in simulations with continuous outcomes and N=20K. Horizontal dashed lines represent the true simulated values. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $p$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS). Colors for LDpred2 models represent the number of chains kept (out of 50). \label{fig:simu_p}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.9\textwidth]{est_p_one_200K}}
	\caption{Inferred polygenicity $p$ in simulations with continuous outcomes and N=200K. Horizontal dashed lines represent the true simulated values. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
		``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
		The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $p$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS). Colors for LDpred2 models represent the number of chains kept (out of 50). \label{fig:simu_p_large}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=0.8\textwidth]{est_alpha_one_20K}}
\caption{Inferred $\alpha$ in simulations with continuous outcomes and N=20K. Horizontal dashed lines represent the true simulated values. Horizontal dotted lines represent boundaries imposed on the LDpred2-auto estimates. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that ``LDpred2\_noMLE'' (\texttt{use\_MLE = FALSE}) does not infer $\alpha$. Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $\alpha$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS). Colors for LDpred2 models represent the number of chains kept (out of 50). \label{fig:simu_alpha}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.8\textwidth]{est_alpha_one_200K}}
	\caption{Inferred $\alpha$ in simulations with continuous outcomes and N=200K. Horizontal dashed lines represent the true simulated values. Horizontal dotted lines represent boundaries imposed on the LDpred2-auto estimates. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that ``LDpred2\_noMLE'' (\texttt{use\_MLE = FALSE}) does not infer $\alpha$. Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. 
		The 95\% confidence intervals for the LDpred2-auto and SBayesS estimates are obtained from the 2.5\% and 97.5\% quantiles of all the $\alpha$ estimates from the iterations (after burn-in) of the chains kept (note that only one chain is used and kept in SBayesS). Colors for LDpred2 models represent the number of chains kept (out of 50). \label{fig:simu_alpha_large}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{postp_calib}}
\caption{LDpred2-auto calibration of per-variant posterior probabilities of being causal (also known as posterior inclusion probabilities) in simulations with continuous outcomes. These probabilities are binned on a log-scale, and mean in each bin is compared to the proportion of simulated causal variants in the bin (with 95\% CI). Green dashed lines represent the 1:1 line. Only results for $\alpha = -0.5$ and \texttt{allow\_jump\_sign = FALSE} are represented. Colors represent the number of chains kept (out of 50). \label{fig:simu_postp_calib}}
\end{figure}

\begin{figure}[p]
\centerline{\includegraphics[width=\textwidth]{local_h2_calib}}
\caption{LDpred2-auto calibration of per-block heritability estimates in simulations with continuous outcomes. 
Local $h^2$ estimate for each block is compared to the true simulated local heritability in the block.
Green dashed lines represent the 1:1 line. Only results for $\alpha = -0.5$ and \texttt{allow\_jump\_sign = FALSE} are represented. Colors represent the number of chains kept (out of 50). \label{fig:simu_h2_calib}}
\end{figure}

@@

\begin{figure}[p]
\centerline{\includegraphics[width=0.9\textwidth]{est_r2_one_20K}}
\caption{Inferred predictive performance $r^2$ in simulations with continuous outcomes and N=20K. Green segments represent $r^2$ in the test set. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. Colors for LDpred2 models represent the number of chains kept (out of 50). \label{fig:simu_r2}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.9\textwidth]{est_r2_one_200K}}
	\caption{Inferred predictive performance $r^2$ in simulations with continuous outcomes and N=200K. Green segments represent $r^2$ in the test set. For LDpred2-auto, suffix ``nojump''/``jump'' refers to using \texttt{allow\_jump\_sign = FALSE/TRUE} (and \texttt{use\_MLE = TRUE}), and 
	``noMLE'' refers to using \texttt{use\_MLE = FALSE} (and \texttt{allow\_jump\_sign = FALSE}), and ``newfilter'' is similar to ``nojump'' but uses a different post-filtering of chains (Methods). Note that the recommended option is to use \texttt{allow\_jump\_sign = FALSE} \cite[]{prive2021identifying}. Colors for LDpred2 models represent the number of chains kept (out of 50). \label{fig:simu_r2_large}}
\end{figure}

@@

\begin{figure}[p]
	\centerline{\includegraphics[width=0.83\textwidth]{est_binary_h2_one}}
	\caption{Inferred SNP heritability $h^2$ in simulations with binary outcomes. Horizontal dashed lines represent the true simulated values. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the $h^2$ estimates from the iterations (after burn-in) of the chains kept. The 95\% confidence interval for the LD Score regression estimate is obtained from $\pm$1.96 times its standard error. Colors for LDpred2 models represent the number of chains kept (out of 50). {\NEFF} All $h^2$ estimates are transformed to the liability scale with K\_pop=K and K\_GWAS either K (the simulated prevalence) or 0.5 (when using Neff) using function \texttt{coef\_to\_liab} from R package bigsnpr \cite{lee2012better,prive2017efficient}. \label{fig:simu_h2_bin}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.9\textwidth]{est_binary_p_one}}
	\caption{Inferred polygenicity $p$ in simulations with binary outcomes. Horizontal dashed lines represent the true simulated values. Colors for LDpred2 models represent the number of chains kept (out of 50). {\NEFF} \label{fig:simu_p_bin}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.83\textwidth]{est_binary_alpha_one}}
	\caption{Inferred $\alpha$ in simulations with binary outcomes. Horizontal dashed lines represent the true simulated values. Horizontal dotted lines represent boundaries imposed on the estimates. Colors for LDpred2 models represent the number of chains kept (out of 50). {\NEFF} \label{fig:simu_alpha_bin}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=0.88\textwidth]{est_binary_r2_one}}
	\caption{Inferred predictive performance $r^2$ in simulations with binary outcomes. Green segments represent $r^2$ in the test set. Colors for LDpred2 models represent the number of chains kept (out of 50). {\NEFF} All $r^2$ estimates are transformed to the liability scale with K\_pop=K and K\_GWAS either K (the simulated prevalence) or 0.5 (when using Neff) using function \texttt{coef\_to\_liab} from R package bigsnpr \cite{lee2012better,prive2017efficient}; the ones from the test set are transformed with K and K. \label{fig:simu_r2_bin}}
\end{figure}

@@

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2}}
	\caption{SNP heritability estimates from either LDpred2-auto or LD Score regression for all 248 phenotypes defined from the UK Biobank. These are stratified by the polygenicity estimated from LDpred2-auto. Green dashed lines represent the 1:1 line. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the $h^2$ estimates from the iterations (after burn-in) of the chains kept. The 95\% confidence interval for the LD Score regression estimate is obtained from $\pm$1.96 times its standard error.  ``use\_mle: TRUE'' corresponds to using the new 3-parameter model and sampling scheme (Methods). Colors represent the number of chains kept for LDpred2-auto (out of 50). \label{fig:ukbb_h2}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2_p}}
	\caption{Estimates from LDpred2-auto for either the SNP heritability $h^2$ or the polygenicity $p$ for all 248 phenotypes defined from the UK Biobank. Estimates of $h^2$ are constrained to be at least 0.001, and at least $10^{-5}$ for $p$. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the estimates from the iterations (after burn-in) of the chains kept. Colors represent the number of chains kept for LDpred2-auto (out of 50). \label{fig:ukbb_h2_p}}
\end{figure}

\begin{figure}[p]
	\centerline{\includegraphics[width=\textwidth]{ukbb_h2_alpha}}
	\caption{Estimates from LDpred2-auto for either the SNP heritability $h^2$ or $\alpha$ for all 248 phenotypes defined from the UK Biobank. The 95\% confidence interval for the LDpred2-auto estimate is obtained from the 2.5\% and 97.5\% quantiles of all the estimates from the iterations (after burn-in) of the chains kept. Colors represent the number of chains kept for LDpred2-auto (out of 50). We only show phenotypes for which there are more than 25 chains kept, because simulations have shown that $\alpha$ estimates are unreliable when a small number of chains is kept (Figure \ref{fig:simu_alpha}). \label{fig:ukbb_h2_alpha}}
\end{figure}
